---
title: "FRRO2Pooled"
author:
- Douglas A. Campbell
output:
  html_document:
    df_print: paged
    code_folding: hide
    keep_md: yes
    fig_caption: yes
    toc: TRUE
    toc_float: TRUE
csl: plos-one.csl
---

# Introduction
Pool [O2] vs. FRRf data from multiple runs.
Import [Chl] data for screening results.


## Set Chunk Options
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "FluorO2"
#Temporary RunDate during auditing
DataIn<- file.path("..","FitData")
DataOut <- file.path("..", "FitData")
CatalogPath <- file.path("~/Dropbox/MURIS/MURIS_catalog.csv")
ChloroGoogle <- "https://docs.google.com/spreadsheets/d/1yhmuv7V0clcLpqlsTYBMtfIcsS8Rp5yjtkRH2ktZwk0/edit#gid=0"


#Chlorophyll RFU calibration
#https://www.dropbox.com/sh/afag5s8oc5d7hpf/AABK56di0J5-5vVoFuIdvDJOa?dl=0
RFUIntercept_ugL = 0.7656
RFUSlope_ugL = 7.064
```

```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
#library(knitr)
#library(zoo)
library(googlesheets4)
library(googledrive)
```

```{r set colours}
Wavelengths_nm = c(445, 470, 505, 535, 590)
Colours_nm = c("darkblue", "dodgerblue", "darkgreen", "yellowgreen",  "darkorange")


names(Colours_nm) <- Wavelengths_nm
Colours_nm

```

# Import MetaData catalog from MURIS
Improve this if we generalize the approach.
```{r}
#MetaData <- read_csv(file = CatalogPath)
```


Read in MetaData catalog from googlesheets 
```{r load Catalog, now as a google sheet}
# gs4_deauth()
# #deauthorizes access to googlesheet
# 
# MetaCatalog <- read_sheet("https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0") %>%
# # sheet is read in by sheet ID, obtained from the URL of the sheet.
# # read_sheet has an annoying "feature" to set the type of columns it can't parse to a list.
# # ggplot/dplyr doesn't like working with a dataframe of lists.
# # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
# # To fix this, first drop all rows missing WL, then unlist.
# # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
# 

# as.data.frame(MetaCatalog)
```

## Read Chlorophyll Data
```{r read chlorophyll data}
gs4_deauth()
ChloroData <- read_sheet(ChloroGoogle)

#convert DATE, TIME
ChloroData <- ChloroData %>%
  mutate(DATE = ymd(DATE))

#volume correction for RFU
#fine calibration table?

ChloroData <- ChloroData %>%
  mutate(Rfu_vol = Reading_rfu * SolventVol_ul/SampleVol_ul)

#collapse Replicates
ChloroDataAver <- ChloroData %>%
  group_by(CultureID, DATE) %>%
  summarize (Chl_rfu_vol_mean = mean(Rfu_vol, na.rm = TRUE), .groups = "keep") %>%
  ungroup()

#convert to Chla_ugL
ChloroDataAver <- ChloroDataAver %>%
  mutate(Chl_ugL = (Chl_rfu_vol_mean - RFUIntercept_ugL)/RFUSlope_ugL)

```

## List O2FRRfData
```{r}
O2FRRfFiles <- list.files(path = DataIn, full.names = TRUE)
O2FRRfFiles
```


## Read O2FRRfData
Many blank rows; consider re-working FRRO2Compare.Rmd
```{r read O2FRRfData}
read_plus_rds = function(Flnm) {readRDS(Flnm) %>% mutate(Filename = Flnm)
           }

O2FRRfPool <- O2FRRfFiles %>%
  map_df(~read_plus_rds(Flnm = .)) %>%
  filter(!is.na(filenameO2))
```


```{r prelimplot}
O2FRRfPool %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = ActPAR, y = O2evln_O2ls, colour = Ex_WL)) +
  #geom_point(aes(x = FRRfData$LR_s, y = FRRfData$JVPSII_aLHIIminmax)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

O2FRRfPool %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  #geom_point(aes(x = ActPAR, y = O2evln_O2ls, colour = Ex_WL)) +
  geom_point(aes(x = ActPAR, y = JVPSII_aLHIIminmax)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  theme_bw()

```

# left_join ChloroDataAver to O2FRRfData

```{r leftjoin ChloroDataAver to O2FRRfData}
O2FRRfPool <- left_join(x = O2FRRfData, y = ChloroDataAver, by = c("CultureID", c("ObsDate" = "DATE")), suffix = c("O2FRRf", "Chl"), keep = FALSE)

```

```{r O2FRRfChlprelimplot}
O2FRRfPool %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(y = O2evln_O2ls, x = JVPSII_aLHIIminmax, size = Chl_ugL)) +
  scale_colour_manual(values = Colours_nm) +
 facet_grid(rows = vars(Ex_WL), cols = vars(strain)) +
  theme_bw()

O2FRRfPool %>%
  filter(Dark1s == 0) %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_aLHIIminmax > 0) %>%
  ggplot() +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_aLHIIminmax, size = Chl_ugL, colour = strain)) +
  facet_grid(rows = vars(Ex_WL)) +
  theme_bw()

```

```{r lm PSIIETR_O2}
#no signifiant effect of strain
tidy(O2FRRfPool %>% 
  filter(Dark1s == 0) %>%
  filter(O2evln_O2ls > 0) %>% 
  filter(JVPSII_aLHIIminmax > 0) %>%
  lm(JVPSII_aLHIIminmax ~ O2evln_O2ls + Ex_WL + strain, data = .))

#significant effect of Ex_WL
tidy(O2FRRfPool %>% 
  filter(Dark1s == 0) %>%
  filter(O2evln_O2ls > 0) %>% 
  filter(JVPSII_aLHIIminmax > 0) %>%
  lm(JVPSII_aLHIIminmax ~ O2evln_O2ls + Ex_WL, data = .))


#could alternately 'nest' by Ex_WL to generate single nested dataframe
PSIIETR_O2_lm_445 <- tidy(O2FRRfPool %>%
  filter(Dark1s == 0) %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_aLHIIminmax > 0) %>%
  filter(Ex_WL == "445") %>%
  lm(JVPSII_aLHIIminmax ~ O2evln_O2ls, data = .))

PSIIETR_O2_lm_445

PSIIETR_O2_lm_590 <- tidy(O2FRRfPool %>%
  filter(Dark1s == 0) %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_aLHIIminmax > 0) %>%
  filter(Ex_WL == "590") %>%
  lm(JVPSII_aLHIIminmax ~ O2evln_O2ls, data = .))

PSIIETR_O2_lm_590
```

```{r PSIIETR_O2_lm_plot}
#{} around ggplot call allow us to use .$ to set Title etc. to values from filtered dataframe
#note '.' in ggplot(.)
 O2FRRfPool %>%
  filter(Dark1s == 0) %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_aLHIIminmax > 0) %>%
  filter(Ex_WL == 445) %>% {
  ggplot(.) +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_aLHIIminmax,size = Chl_ugL, colour = strain)) +
  geom_abline(intercept = PSIIETR_O2_lm_445$estimate[1], slope = PSIIETR_O2_lm_445$estimate[2]) +
  geom_abline(intercept = PSIIETR_O2_lm_445$estimate[1] + PSIIETR_O2_lm_445$std.error[1], slope = PSIIETR_O2_lm_445$estimate[2] + PSIIETR_O2_lm_445$std.error[2], linetype = "dashed") +
    geom_abline(intercept = PSIIETR_O2_lm_445$estimate[1] - PSIIETR_O2_lm_445$std.error[1], slope = PSIIETR_O2_lm_445$estimate[2] - PSIIETR_O2_lm_445$std.error[2], linetype = "dashed") +
  labs(title =  paste("Ex_WL ", unique(.$Ex_WL), "nm")) +
  theme_bw()}


 O2FRRfPool %>%
  filter(Dark1s == 0) %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_aLHIIminmax > 0) %>%
  filter(Ex_WL == 590) %>% {
  ggplot(.) +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_aLHIIminmax,size = Chl_ugL, colour = strain)) +
  geom_abline(intercept = PSIIETR_O2_lm_590$estimate[1], slope = PSIIETR_O2_lm_590$estimate[2]) +
  geom_abline(intercept = PSIIETR_O2_lm_590$estimate[1] + PSIIETR_O2_lm_590$std.error[1], slope = PSIIETR_O2_lm_590$estimate[2] + PSIIETR_O2_lm_590$std.error[2], linetype = "dashed") +
    geom_abline(intercept = PSIIETR_O2_lm_590$estimate[1] - PSIIETR_O2_lm_590$std.error[1], slope = PSIIETR_O2_lm_590$estimate[2] - PSIIETR_O2_lm_590$std.error[2], linetype = "dashed") +
  labs(title = paste("Ex_WL ", unique(.$Ex_WL), "nm")) +
  theme_bw()}
 
  O2FRRfPool %>%
  filter(Dark1s == 0) %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_aLHIIminmax > 0) %>%
  filter(Ex_WL == 590) %>% {
  ggplot(.) +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_aLHIIminmax,size = Chl_ugL, colour = salinity)) +
  geom_abline(intercept = PSIIETR_O2_lm_590$estimate[1], slope = PSIIETR_O2_lm_590$estimate[2]) +
  geom_abline(intercept = PSIIETR_O2_lm_590$estimate[1] + PSIIETR_O2_lm_590$std.error[1], slope = PSIIETR_O2_lm_590$estimate[2] + PSIIETR_O2_lm_590$std.error[2], linetype = "dashed") +
    geom_abline(intercept = PSIIETR_O2_lm_590$estimate[1] - PSIIETR_O2_lm_590$std.error[1], slope = PSIIETR_O2_lm_590$estimate[2] - PSIIETR_O2_lm_590$std.error[2], linetype = "dashed") +
  labs(title = paste("Ex_WL ", unique(.$Ex_WL), "nm")) +
  theme_bw()}


O2FRRfPool %>%
  filter(Dark1s == 0) %>%
  filter(O2evln_O2ls > 0) %>%
  filter(JVPSII_aLHIIminmax > 0) %>%
  #filter(Ex_WL == 590) %>% {
  {ggplot(.) +
  geom_point(aes(x = O2evln_O2ls, y = JVPSII_aLHIIminmax,size = Chl_ugL, colour = strain, shape = Ex_WL)) +
  geom_abline(intercept = PSIIETR_O2_lm_590$estimate[1], slope = PSIIETR_O2_lm_590$estimate[2]) +
  geom_abline(intercept = PSIIETR_O2_lm_590$estimate[1] + PSIIETR_O2_lm_590$std.error[1], slope = PSIIETR_O2_lm_590$estimate[2] + PSIIETR_O2_lm_590$std.error[2], linetype = "dashed") +
    geom_abline(intercept = PSIIETR_O2_lm_590$estimate[1] - PSIIETR_O2_lm_590$std.error[1], slope = PSIIETR_O2_lm_590$estimate[2] - PSIIETR_O2_lm_590$std.error[2], linetype = "dashed") +
 geom_abline(intercept = PSIIETR_O2_lm_445$estimate[1], slope = PSIIETR_O2_lm_445$estimate[2]) +
  geom_abline(intercept = PSIIETR_O2_lm_445$estimate[1] + PSIIETR_O2_lm_445$std.error[1], slope = PSIIETR_O2_lm_445$estimate[2] + PSIIETR_O2_lm_445$std.error[2], linetype = "dashed") +
    geom_abline(intercept = PSIIETR_O2_lm_445$estimate[1] - PSIIETR_O2_lm_445$std.error[1], slope = PSIIETR_O2_lm_445$estimate[2] - PSIIETR_O2_lm_445$std.error[2], linetype = "dashed") +
  theme_bw()}

```




```{r save O2FRRfMeta}
saveRDS(O2FRRfPool, file.path(DataOut, paste(Project, "O2FRRfPool.Rds", sep = "_"), fsep = .Platform$file.sep))
```


