---
title: "O2ImportTidy"
author: "Douglas A. Campbell, Max Berthold, Laurel Genge"
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
---

##Introduction

##Hypotheses
 1. change in oxygen and Reactive Oxygen Species concentrations differentially alter the growth of different strains of picophytoplankton derived from different ocean habitats
 2. Reactive oxygen species stimulate growth of some picophytoplankton strains.
 


## Materials and Methods

This .Rmd Rworkbook imports data in simple .csv form exported from PSI Multicultivators based upon project specific values for variables set by the user.

It tidies and organizes the data.
It imports a metadata Catalog and merges the metadata with the imported data from "Pico-> O2Data"


To-Do list:

variable name is in two rows, need to find a way to make variable name in two rows into one row.
Need to match the tube number from file name with Ch1O2 etc... 
Need to match each run with date from catalog
create preiminary graphs

#Priority List
Laurel:
-single data file import for O2
-multi-file batch data import (may not be fully feasible given we need match multiple files together in some cases)
-O2 preliminary plots
-merge O2 plots as over-lays of growth plots (time axis may be tricky but I think I know how)




```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..","O2Data")
PlotsPath <- file.path("..","Plots")
DataOut <- file.path("..","ProcessData")
#MetaCatalog <- file.path("..","PicoCatalog.csv")

FileEncode <- "UTF-8" 
Delimiter <- "\t"
#this is brittle; better to figure out how to read all data starting at line that contains 'key'
HeaderRows <- 19
Comment <- "#"

```

```{r, install packages}
# install.packages('googlesheets4')
# install.packages('googledrive')
# install.packages('dplyr')
```

```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
#library(zoo)
library(tidyquant)
library(googlesheets4)
library(googledrive)
#library(dplyr)
```


This chunk reads in the MetaData catalog from googlesheets 
```{r load Catalog, now as a google sheet}
gs4_deauth()
#deauthorizes access to googlesheet

MetaCatalog <- read_sheet("https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0") %>%
# sheet is read in by sheet ID, obtained from the URL of the sheet.
# read_sheet has an annoying "feature" to set the type of columns it can't parse to a list.
# ggplot/dplyr doesn't like working with a dataframe of lists.
# In this case WL is set to a list since some values are numbers, some are strings, some are blank.
# To fix this, first drop all rows missing WL, then unlist.
# Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.

drop_na(WL) %>%
  mutate(WL = unlist(WL))

as.data.frame(MetaCatalog)
```

Tidy the catalog, making dates as date values, tube as character, and wavelenth as a character
```{r}
TidyCatalog <- MetaCatalog %>%
  mutate(InnocDate = ymd(InnocDate),
         ExpDate = ymd(ExpDate), 
         Tube = as.character(Tube)) %>% 
  select(-c(PrimaryOperator, Description, Motivation, doi, Source, SourceSalinity, Plate, Well))

#Catalog <- MetaCatalog %>%
  #mutate(InnocDate = ymd(InnocDate),
         #ExpDate = ymd(ExpDate),
         #Tube = as.character(Tube)) %>%
  #select(-c(PrimaryOperator, Description, Motivation, doi))

#check catalog for correct selections

  TidyCatalog
```

```{r, subsetting catalog for run 14}
TargetRun = 14
RunCatalog <- select(filter(TidyCatalog, Run == TargetRun),c(Run:Optode))

RunCatalog 

```

listing the names of the oxygen data, classified as DataIn. DataIn = O2Data 
```{r O2Data files}

O2DataFiles <- list.files(path = DataIn, pattern = Project, full.names = TRUE)

#check file names
O2DataFiles
```

Creates function using data.table::fread to skip the beginning comments and starts reading file after key word "Data". Seconf function read_tsv_plus adding file name and skips header rows to start reading file after. Data read.delim_plus or read_delim_plus adds filename and cdate, message=FALSE, warning=FALSE
```{r creating two functions to read in data}

#function adds filename and cdate and controls when R starts to read the file, skips header rows
fread_plus <- function(Flnm, Skip){data.table::fread(file = Flnm, skip = "Date" ) %>% mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(Flnm)$ctime))}


#function allows you to read in oxygen data files (Reads in Run14 files)
read_tsv_plus <- function(Flnm, HeaderRows){read_tsv(Flnm,  col_names = TRUE,  skip = HeaderRows) %>%
    mutate(filename = Flnm)}

#generates a read function using tidyverse::read_delim
 #read.delim_plus <- function(flnm, FileEncode, Delimiter, HeaderRows){read.delim(flnm, fileEncoding = FileEncode, sep = Delimiter,  skip = HeaderRows, row.names = NULL) %>%
     #mutate(filename = flnm, cdatetime = ymd_hms(file.info(flnm)$ctime))}

#Adds filename and cdate
#read_delim_plus <- function(Flnm, Delimiter, HeaderRows, Comment){read_delim(file = Flnm, delim = Delimiter, comment = Comment, skip = HeaderRows) %>%
     #mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(Flnm)$ctime))}
 
```


Reads in O2Data, and skips the "notes" at the beginning of the data and begins to read after HeaderRows. Renames columns so there are no duplicates (.name_repair)
```{r Test Reading in O2Data}

O2DataTest <- O2DataFiles %>% 
  map_df(~read_tsv_plus(Flnm = ., HeaderRows = 19))

%>%
  select(c(1:3, 5:9)) %>%
  .name_repair = ~c(Ch1O2 = Ch1, 
         Ch2O2 = Ch2, 
         Ch3O2 = Ch3, 
         Ch4O2 = Ch4,
         Temp_C = 'Ch 1',
         AbsoluteTime = 'Time (HH:MM:SS)',
         Time = 'Time (s)')
  select(-c(V5)) %>%
  filter(!is.na(value))

# O2DataTest <- O2DataFiles %>%
#   map_df(~read_tsv_plus(flnm = ., HeaderRows)) #%>%
#   select(c(Date, Time(HH:MM:SS), Time(s), Ch1, Ch2, Ch3, Ch4, Ch 1)) %>%
#   rename(Ch1O2 = Ch1, 
#          Ch2O2 = Ch2, 
#          Ch3O2 = Ch3, 
#          Ch4O2 = Ch4,
#          Temp_C = 'Ch 1',
#          AbsoluteTime = 'Time (HH:MM:SS)', 
#          Time = 'Time (s)' )
#   
# O2DataTest <- O2DataFiles %>% 
#     read_tsv(file = ., col_names = TRUE, skip =  HeaderRows) %>% 
#     select(c(Date, Time(HH:MM:SS), Time(s), Ch1, Ch2, Ch3, Ch4, Ch 1)) %>%
#           rename(Ch1O2 = Ch1,  
#            Ch2O2 = Ch2,  
#            Ch3O2 = Ch3,  
#            Ch4O2 = Ch4, 
#            Temp_C = 'Ch 1')
  #map_df(~
  
#O2DataTest <- O2DataFiles %>% 
  #map_df(~data.table::fread(file = ., skip = "Data")) #%>%
  #select(-c(V5)) #%>%
  #filter(!is.na(value))

# O2Data <- O2DataFiles %>% 
#    map_df(~read_tsv(file = ., col_names = TRUE, skip =  HeaderRows)) %>% 
#   select(c(1:3, 5:10)) %>%
#   rename(Ch1O2 = Ch1, 
#          Ch2O2 = Ch2, 
#          Ch3O2 = Ch3, 
#          Ch4O2 = Ch4,
#          Temp_C = 'Ch 1')

#O2Data <- O2DataFiles %>%
  #map_df(~read_tsv_plus(flnm = ., HeaderRows)) #%>%
  #select(c(1:3, 5:9)) %>%
  #rename(Ch1O2 = Ch1, 
         #Ch2O2 = Ch2, 
         #Ch3O2 = Ch3, 
         #Ch4O2 = Ch4,
         #Temp_C = 'Ch 1',
         #AbsoluteTime = 'Time (HH:MM:SS)', 
         #Time = 'Time (s)' ) 
 
#O2DataTest[1:10,]

#O2DataTest[1:10]



```

This chunk imports first Run 14 file 
```{r read in data}

#function allows you to read in oxygen data files
read_tsv_plus <- function(Flnm, HeaderRows){read_tsv(Flnm,  col_names = TRUE,  skip = HeaderRows) %>%
    mutate(Filename = Flnm)}


#Think about names of time variables in MultiCulti import; we may use E_hour etc.
Run14Data1 <- read_tsv_plus(Flnm = "../O2Data/20200627_PICO_MCMIX006_1234_RUN14.txt", HeaderRows = 19) %>%
  select(c("Date":"Time (s)", "Ch1":"Ch 1", "Filename")) %>%
  rename(Ch1O2 = Ch1, 
         Ch2O2 = Ch2, 
         Ch3O2 = Ch3, 
         Ch4O2 = Ch4,
         Temp_C = 'Ch 1',
         AbsoluteTime = 'Time (HH:MM:SS)',
         Time_s = 'Time (s)') %>%
  mutate(E_hour = Time_s/3600)

#Extract Run number from filename using REGEX, possibly with str_extract or grep
Run14Data1 <- Run14Data1 %>%
  mutate(Run = str_extract(string = Filename, pattern = "RUN14.txt"),
         Run = str_remove(string = Run, pattern = "RUN"),
         Run = str_remove(string = Run, pattern = ".txt")) 

#Check Data File  
Run14Data1

```

Pivot long function changes rows to columns and vice versa
```{r pivot long}
Run14Data1long <- Run14Data1 %>%
  pivot_longer(., cols =  c(4:7), names_to = "Channel", values_to = "O2_umolL") 

Run14Data1long <- Run14Data1long %>% 
  mutate(Tube = case_when(str_detect(Channel, "Ch1O2") ~ 1,
                          str_detect(Channel, "Ch2O2") ~ 2, 
                          str_detect(Channel, "Ch3O2") ~ 3, 
                          str_detect(Channel, "Ch4O2") ~ 4)) %>% 
  mutate(Tube = as.character(Tube))

#Check files
Run14Data1long
```

Imports second run 14 file
```{r importing file 2}

Run14Data2 <- read_tsv_plus(Flnm = "../O2Data/20200627_PICO_MCMIX006_5678_RUN14.txt", HeaderRows = 19) %>%
  select(c("Date":"Time (s)", "Ch1":"Ch 1", "Filename")) %>%
  rename(Ch1O2 = Ch1, 
         Ch2O2 = Ch2, 
         Ch3O2 = Ch3, 
         Ch4O2 = Ch4,
         Temp_C = 'Ch 1',
         AbsoluteTime = 'Time (HH:MM:SS)',
         Time_s = 'Time (s)') %>%
  mutate(E_hour = Time_s/3600) 

 Run14Data2 <- Run14Data2 %>%
   mutate(Run = str_extract(string = Filename, pattern = "RUN14.txt"),
         Run = str_remove(string = Run, pattern = "RUN"),
         Run = str_remove(string = Run, pattern = ".txt")) 

#Check Data File  
Run14Data2

Run14Data2long <- Run14Data2 %>%
  pivot_longer(., cols =  c(4:7), names_to = "Channel", values_to = "O2_umolL") 

Run14Data2long <- Run14Data2long %>% 
  mutate(Tube = case_when(str_detect(Channel, "Ch1O2") ~ 5,
                          str_detect(Channel, "Ch2O2") ~ 6, 
                          str_detect(Channel, "Ch3O2") ~ 7, 
                          str_detect(Channel, "Ch4O2") ~ 8)) %>% 
  mutate(Tube = as.character(Tube))

#Check files
Run14Data2long

```



This Chunk merges both Run 14 data files together in long format
```{r merging data files}

O2DataMergeRun14 <- rbind(Run14Data1long, Run14Data2long)

```

```{r Merging Run14 Data and MetaCatalog}

#extract ExpDate for matching with Catalog
# O2DataMerge <- O2Data %>% 
#     mutate(InnocDate = str_extract(Date, "2020-06-26"),
#            InnocDate = ymd(str_extract(InnocDate, "2020-06-26")))

#extract MC for matching with Catalog
#will break with white MC; think about it.
#MultiData <- MultiData %>% 
    #mutate(MC = str_extract(Filename, "MCMIX[:digit:][:digit:][:digit:]"))

#add ln(value) later

#Merges Run14Datalong 1 only
O2DataMergeMeta <- left_join(x = O2DataMergeRun14, y = Run14Catalog, by = c("Tube", "Run"))

#Check Merge
O2DataMergeMeta

```

Setting names for variables
```{r naming variables}

# Run <- c("../O2Data/20200129_PICO_MCMIX006_RUN4.txt", "../O2Data/20200130_PICO_MCMIX006_RUN4.txt")
# Sensor <- "od-680"
# 
# RunDate ="2020-01-29"

```
 
```{r set colours}
MyWavelengths = c(405, 450, 475, 530, 615, 660, 730, "WW")
MCMIXColours = c("violet", "darkblue", "dodgerblue", "green","orange","red","purple", "black")

names(MCMIXColours) <- MyWavelengths
MCMIXColours
```

```{r preliminary plots}

O2DataPlot <- O2DataMerge %>%
  # filter(grepl(O2_umolL, key)) %>%
  # filter(grepl("od-sensors-", key)) %>%
  ggplot() +
  geom_point(aes(x = Time, y = O2_umolL, colour = as.factor(WL))) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(cols = vars(as.factor(O2)), rows = vars(as.factor(Par_ue),Strain)) +
  theme_bw() +
  labs(y = "Oxygen Concentration", title = "Run Date 2020-06-26") #caption = paste(Run[1], Run[2], sep = "_"))

 # filter(ExpDate == RunDate) %>%
    
O2DataPlot

```

This graph plots the oxygen concentration (umol O2/L) data from Run14 against time elapsed in seconds. The two faccets separate the light intesity between the two growth conditions. The colour of the dots correspond with the colour of light that the cells were exposed to. This culture was grown with no oxygen added. Therefore all oxygen plotted here is oxygen created through respiration of the prochlorococcus. 

To improve this graph:
- Have the light level change able to be graphed with the chnging oxygen concentration 
- Put this data over top of the growth data Carlie has plotted
- Compare this data to other strains under the same conditions (low oxygen, blue and red light, 60 and 30 ue)
- load in all other O2 data to get better representation of oxygen concentrations
- Add a caption embedded in the code so it is not dead end graph





