---
title: "SolisenseImport"
author:
- Maximilian Berthold
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
    code_folding: hide
    keep_md: yes
    fig_caption: yes
    toc: TRUE
    toc_float: TRUE   
csl: plos-one.csl
---

*Some of the code used to create this R Notebook was refurbished from "PlateAbImport.Rmd" written by Maximilian Berthold, Douglas A. Campbell, Melissa L. Rioux, Sarah J Gore, and Alyson MacCormack.*


# Set Chunk Options
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Set Project Variables
```{r set project variables}
Project <- "FluorO2"
DataOut <- file.path("..", "ImportData")

#Move catalog to Googlesheets?
#We need to figure out the catalog issue
Catalog <- file.path("~/Dropbox/MURIS/MURIS_catalog.csv")

# gs4_deauth()
# ColonyData <- read_sheet(ColonyGoogleSheet)
# 
# ColonyData

#FileIDAb <- "Ab"
#FileIDSoli <- "_Soli_"
#FileReadSoli <- "Soli"
#DataFolder <- "ProcessData"

DataIn <- file.path("..", "RawData", "Solisense", fsep = .Platform$file.sep)

FileID <- "fit"

FileEncode <- "UTF-8" 
Delimiter <- ","

HeaderRows <- 0
#AbsWL = c(440, 590, 680, 750) #select OD's of interest from plategrowth.Rds



```


```{r load libraries}
library(tidyverse)
library(lubridate)
#library(magrittr)

#https://googlesheets4.tidyverse.org/
# library(googledrive)
# library(googlesheets4)

```


```{r load local catalog, message = FALSE, warning = FALSE, echo=FALSE}
#col_types specified for some columns as only the last few rows of a large dataset contained values for these columns and the values were not being read in properly
#there is probably a more robust way to deal with this issue
# MetaData <- read_csv("../MURIS_catalog.csv") %>%
#   rename(CultureID = id)
# 
# MetaData <- MetaData %>%
#   mutate(ExpSalinity = (((culture_inocul_L * source_salinity)+(media_inocul_L*salinity))/(culture_inocul_L+media_inocul_L)))
# 
# GrowthLong <- readRDS(file = file.path(DataFolder,paste(Project,FileIDAb, "GrowthLong.Rds", sep  = "_"),fsep = .Platform$file.sep)) %>%
#   rename(CultureID = id, StartDateTimeInoc = datetime) %>%
#   #filter(E_hours == '0') %>% #select only E-hour == 0, as starting point for plate inoculation and following Solisense-analyses
#   filter(Wavelength %in% AbsWL) %>%
#   mutate(ObsDate = format(StartDateTimeInoc, format = "%Y-%m-%d")) %>%
#   mutate(ObsDate = ymd(ObsDate))
# 
# MetaGrowthData <- full_join(MetaData, GrowthLong) %>%
#   filter(E_hours != 'NA')
# 
# MetaGrowthData <- MetaGrowthData %>%
#   select(-c(OD, AvBlankOD, blank, plc, plc_vol)) %>%
#   pivot_wider(values_from = CorrOD, names_from = Wavelength, names_prefix = "OD_")

```

```{r set colours}
Wavelengths_nm = c(445, 470, 505, 535, 590)
Colours_nm = c("darkblue", "dodgerblue", "darkgreen", "yellowgreen",  "darkorange")


names(Colours_nm) <- Wavelengths_nm
Colours_nm

```

```{r list PSI files for file import}
SolisenseFiles <- list.files(path = DataIn, pattern = FileID, full.names = TRUE)
SolisenseFiles

#test for duplicate file names
unique(duplicated(SolisenseFiles))
```


```{r data read adds filename and cdate, warning=FALSE, message=FALSE, echo=FALSE}
#design choice 2 file reading functions or add a filetype variable to a single function
#stringsAsFactors =FALSE somewhere? 

read.delim_plus <- function(flnm, file_encode, delimiter, header_rows){read.delim(flnm, fileEncoding = file_encode, sep = delimiter,  skip = header_rows, row.names = NULL) %>% mutate(filename = flnm, cdatetime = ymd_hms(file.info(flnm)$ctime))
}

```

Read Test File
```{r read example Solisense file}
#issue with rows with --------;  easy to filter though
# TestFile <- read.delim_plus(flnm = "../RawData/Solisense/MURIS_202105121400_MaBe3414_445_caloxy_fit.csv", file_encode = FileEncode, delimiter = Delimiter, header_rows = HeaderRows)

```

purrr::map to read all files
```{r read Solisense files}
SolFits <- SolisenseFiles %>%
  map_df(~read.delim_plus(flnm =., file_encode = FileEncode, delimiter = Delimiter, header_rows = HeaderRows))
```


```{r tidy SolFitsTrim}
#Think of better ways to do this
SolFitsTrim <- SolFits %>% 
  filter(!grepl("----", DATE)) %>% # remove rows with "----"
  select(-c("Lon", "Lat", "GPS_stat")) %>% # remove superfluous columns
  mutate(filename = str_remove(string = filename, pattern = ".csv")) %>%
  mutate(filename = str_remove(string = filename, pattern = "../RawData/")) %>%
  separate(filename, into = c("Device", "Project", "DateTime", "CultureID", "Ex_WL", "Exp_Type"), sep = "([\\/\\_\\_\\_\\_])", remove = FALSE) %>%
  mutate(DATE = ymd(DATE),
          TIME = as.character(TIME)) %>% #time-column is read in as factor, and as.character changes it to numeric; using lubdridate::hms would only change the format to 13H 4M 2S but does not work later one to merge into one DateTime-column
  rename(ObsDate = DATE,
         ObsTime = TIME,
         FvFm = "Fv.Fm") %>%
  mutate(DateTime = as.numeric(DateTime),
         Ex_WL = as.factor(as.numeric(Ex_WL))) %>%
  mutate(FvFm = as.numeric(as.character(FvFm)),
         nm445 = as.numeric(as.character(Light_1)),
         nm590 = as.numeric(as.character(Light_5))) %>%
  mutate(datetime = ymd_hm(DateTime)) %>%
  rename(StartDateTimeSol = DateTime) %>%
  drop_na(StartDateTimeSol) %>%
  mutate(ObsTime = hms(ObsTime)) %>%
  mutate(ObsDateTime = ymd_hms(paste(ObsDate, ObsTime))) %>%
  relocate(ObsDateTime, .after = ObsTime) %>%
  relocate(CultureID, .before = ObsDate) 

SolFitsTrim <- SolFitsTrim %>%
  mutate(across(.cols = c(Light_1:p680Q), .fns = as.numeric)) %>%
  mutate(ActPAR = Light_1 + Light_2 + Light_3 + Light_4 + Light_5 + Light_6) #better ways to do this?

SolFitsTrim[1,]

#XXXX Working on separating 1 s dark rows from other rows; perhaps filter all rows where time increment < 2 s?

#generate column with duration of light step in s

#add a column adding Dark1s based upon any step < 5 s
#replace NA for first dark with nominal 181;  issue will be changing durations of light steps across each run
SolFitsTrim <- SolFitsTrim %>%
  group_by(Source.DataFile, CultureID, Ex_WL) %>%
  #mutate(Step_s = as.numeric(ObsDateTime - lag(ObsDateTime)), .after = ObsDateTime) %>%
  mutate(Step_s = replace_na(as.numeric(ObsDateTime - lag(ObsDateTime)), 181), .after = ObsDateTime) %>%
  mutate(LR_s = as.numeric(ObsDateTime - ObsDateTime[1]), .after = Step_s) %>%
  mutate(Dark1s = if_else(Step_s > 5, 0, 1), .after = Step_s) %>%
  relocate(Ex_WL, .after = Dark1s) %>%
  relocate(ActPAR, .after = Ex_WL)


#Figure out how to cope with final step at 0 PAR, not followed by Dark1s step
#separate Dark1s rows


#Figure out how to re-match Dark1s to appropriate light steps

```



```{r prelimplots}
SolFitsTrim %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = ActPAR, y = FvFm, colour = Ex_WL, size = LR_s)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  theme_bw()

SolFitsTrim %>%
  #filter(Dark1s != 0) %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = FvFm, colour = Ex_WL, size = ActPAR)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  theme_bw()

```

unique(SolFitsTrim$LR_s)

```{r estimate parameters}
#think about nest_by and map?
SolFitsTrim <- SolFitsTrim %>%
  group_by(CultureID, Ex_WL, Source.DataFile) %>%
  mutate(Fodark = Fo[1],
         Fmdark = Fm[1],
         aLHIIdark = (Fmdark * Fodark)/(Fmdark - Fodark),
         Fomin = min(Fo, na.rm = TRUE),
         Fmmax = max(Fm, na.rm = TRUE),
         aLHIIminmax = (Fmmax * Fomin)/(Fmmax - Fomin),
         Sig_m2psii = Sig/1E20,
         ActPAR_photonsm2s = ActPAR *  6.022e17,
         Ctau1 = 1/(1 + (Sig_m2psii * ActPAR_photonsm2s * (Tau1QA/1000000))),
         Ctau2 = 1/(1 + (Sig_m2psii * ActPAR_photonsm2s * (Tau2QA/1000000))),
         qp = (Fm - Fo)/(Fm - Fomin), #improve this with Fo1s
         JVPSII_aLHIIminmax = ActPAR_photonsm2s * aLHIIminmax * FvFm) %>%
  ungroup()


  #mutate(aLHII <- 
```

```{r prelimplots2}
SolFitsTrim %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = ActPAR, y = aLHIIdark, colour = Ex_WL)) +
  geom_point(aes(x = ActPAR, y = aLHIIminmax), shape = "cross") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  theme_bw()

SolFitsTrim %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = Ctau1, y = qp, colour = Ex_WL)) +
  #geom_point(aes(x = ActPAR, y = aLHIIminmax), shape = "cross") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  coord_fixed(ratio = 1) +
  theme_bw()

SolFitsTrim %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = Ctau2, y = qp, colour = Ex_WL)) +
  #geom_point(aes(x = ActPAR, y = aLHIIminmax), shape = "cross") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  coord_fixed(ratio = 1) +
  theme_bw()

SolFitsTrim %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = ActPAR, y = JVPSII_aLHIIminmax, colour = Ex_WL)) +
  #geom_point(aes(x = ActPAR, y = aLHIIminmax), shape = "cross") +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  theme_bw()

```


```{r save SolFitsTrim data}
saveRDS(SolFitsTrim, file.path(DataOut, paste(Project, "SolFitsTrim.Rds", sep = "_"), fsep = .Platform$file.sep))
```

XXXXXX



 )%>% #time-column is read in as factor, and as.character changes it to numeric; using lubdridate::hms would only change the format to 13H 4M 2S but does not work later one to merge into one DateTime-column
  rename(ObsDate = DATE, ObsTime = TIME, FvFm = "Fv.Fm") %>%
  mutate(datetime = as.numeric(datetime), Ex_WL = as.factor(as.numeric(Ex_WL))) %>%
  mutate(FvFm = as.numeric(as.character(FvFm)), Light_1 = as.numeric(as.character(Light_1)), Light_5 = as.numeric(as.character(Light_5))) %>%
  mutate(datetime = ymd_hm(datetime)) %>%
  rename(StartDateTimeSol = datetime) %>%
  drop_na(StartDateTimeSol)

```{r read data from rds}
###### only run, when new files were added, takes very long with >4500 files

# SolFit <- readRDS(file = file.path(DataFolder,paste(Project, FileReadSoli, "SolisenseFiles.Rds", sep  = "_"),fsep = .Platform$file.sep)) 
```

XXXXX


 
#Light steps of Ex445 and 590 are not aligned, as SOLISENSE protocol saved Light-levels of 445 in Light_1 and of 590 in Light_5

SolFit_445 <- SolFitTrim %>%
  filter(Ex_WL == 445) %>%
  mutate(Light_steps = Light_1 + Light_5)

SolFit_590 <- SolFitTrim %>%
  filter(Ex_WL == 590) %>%
  mutate(Light_steps = Light_1 + Light_5)

SolFitAlign <- full_join(SolFit_590, SolFit_445)

SolFitMeta <- right_join(SolFitAlign, MetaData)

SolFitMetaGrowth <- right_join(SolFitAlign, MetaGrowthData, by = c("CultureID", "ObsDate")) %>%
  mutate(EDays = E_hours/24)
  #drop_na(StartDateTime) 

saveRDS(SolFitMetaGrowth, file.path(DataOut, 
paste(Project, "SolFit.Rds", sep = ""), fsep = .Platform$file.sep))


SolFitETR <- SolFitMetaGrowth %>%
  mutate(Sig = as.numeric(Sig), Light_steps = as.numeric(Light_steps), Tau1QA = as.numeric(Tau1QA)) %>%
  mutate(Sig_m2 = Sig*1e-18, 
         Tau1QA_s = Tau1QA/1000,
         Light_steps_Photm2s = Light_steps*6.022e17) %>%
  mutate(One_C = 1/(1+(Sig_m2*Light_steps_Photm2s*Tau1QA_s)), 
         ETRTAU = Light_steps_Photm2s*Sig_m2*One_C)

range(SolFitETR$One_C, na.rm = TRUE)
range(SolFitETR$ETRTAU, na.rm = TRUE)
range(SolFitETR$Tau1QA, na.rm = TRUE)

SolFitETR %>%
  ggplot() +
  geom_point(aes(x = Light_steps, y = ETRTAU, color = par_ue)) +
  facet_grid(cols = vars(as.factor(Ex_WL))) 

```



```{r}

test3 <- test2 %>%
  drop_na(Ex_WL, ObsDateTime)

test4 <- rbind(test3, 
               test3 %>% 
                 filter(Light_steps == 320))

test3 <- rbind(test2,
      test2 %>% 
        filter(Light_steps == 320)) %>%
  arrange(ObsDateTime) %>%
  group_by(Ex_WL, CultureID, StartDateTimeSol) %>%
  nest() %>%
  mutate(NoRow = map_dbl(data, nrow)) %>%
  filter(NoRow != 22)

test4 <- test2 %>%
  distinct() %>%
  group_by(Ex_WL, CultureID, StartDateTimeSol) %>%
  nest() %>%
  mutate(NoRow = map_dbl(data, nrow)) %>%
  filter(NoRow != 21) %>%
  drop_na(StartDateTimeSol)
  
    
test6 <- test3 %>%
  group_by(Ex_WL, CultureID, StartDateTimeSol) %>%
  nest() %>%
  mutate(NoRow = map_dbl(data, nrow))

test4 <- test3 %>%
  filter(NoRow != 22)
 
test7 <- test6 %>%
  filter(NoRow !=22)

```



```{r select light levels}


#select first all 0-light measurements, select every n-th 0-position, as start value and store as index
#select every 320-light measurement and store as index
#filter every value that is equally smaller/larger then the value before/after to get increasing and decreasing light steps separated 
#bind with 320-light measurements, and first/last 0-light measurement for total set of doubletap-experiment

SolFitLightUP <- SolFitMetaGrowth %>%
  filter(Light_steps > lag(Light_steps)) %>% #filter up to light step 160 and down again, filters out all 0 and 320
   filter(Light_steps < lead(Light_steps)) #filter out second site of double tap protocol

SolFitLight320 <- SolFitMetaGrowth %>%
  filter(Light_steps == 320)

SolFitLong <- rbind(SolFitLightUP, SolFitLight320) #bind light steps 320 and first site of double tap protocol

SolFitShortUP <- SolFitMeta %>%
  filter(Light_steps > lag(Light_steps)) %>% #filter up to light step 160 and down again, filters out all 0 and 320
   filter(Light_steps < lead(Light_steps)) #filter out second site of double tap protocol

SolFitShort320 <- SolFitMeta %>%
  filter(Light_steps == 320)

SolFitShort <- rbind(SolFitShortUP, SolFitShort320) %>%
  group_by(exp_date, strain, source) %>% #group_by ExpDate and salinity to show replicated wells within one consecutive plot, even with different CultureID's
   mutate(EHours = as.numeric((ObsDateTime - ObsDateTime[1])/3600)) %>%  #group by well, then filter light/dark FvFm, then filter max FvFm and compare to growth light
   mutate(EDays = EHours/24) %>%
   ungroup()

# 
# 
# SolFitMeta <- SolFitMeta %>%
#   group_by(exp_date, strain, source) %>% #group_by ExpDate and salinity to show replicated wells within one consecutive plot, even with different CultureID's
#   mutate(EHours = as.numeric((ObsDateTime - ObsDateTime[1])/3600)) %>%  #group by well, then filter light/dark FvFm, then filter max FvFm and compare to growth light
#   mutate(EDays = EHours/24) %>%
#   ungroup()




```



```{r plot data}
# ExpDate <- c(20200930)
# EndDate <- c(20200910)
# culture <- c('MaBe2004', 'MaBe2005', 'MaBe2006', 'MaBe2007', 'MaBe2008', 'MaBe2009')
# Strains = c("CZS25K", "CCMP1333", "CCMP836", "NIES981", "CZS48M")
# strain_source = c('AlMa1495')
# Media = 'BG11+Na2CO3'
# PAR = 160
# Plate = c(163:165)

cols = c(20:59)
SolFitLong[,cols] %<>% lapply(function(x) as.numeric(as.character(x)))

OneStrain = "CZS48M"
LowLightStep = 40
MedLightStep = 160
HighLightStep = 320
LowLight = 30
MedLight = 150
HighLight = 300
PhoPhysVar = "Sigma"

  
PhotoPhysLowLight <- SolFitLong %>%
  filter(strain == OneStrain) %>%
  filter(Light_steps == LowLightStep) %>%
  #filter(source_salinity == 36) %>%
  mutate(par_ue = as.factor(par_ue)) %>%
  filter(par_ue == LowLight) 

PhotoPhysMedLight <- SolFitLong %>%
  filter(strain == OneStrain) %>%
  filter(Light_steps == MedLightStep) %>%
  #filter(source_salinity == 36) %>%
  mutate(par_ue = as.factor(par_ue)) %>%
  filter(par_ue == MedLight)

PhotoPhysHighLight <- SolFitLong %>%
  filter(strain == OneStrain) %>%
  filter(Light_steps == HighLightStep) %>%
  #filter(source_salinity == 36) %>%
  mutate(par_ue = as.factor(par_ue)) %>%
  filter(par_ue == HighLight)

PhotoPhysSal <- ggplot(PhotoPhysLowLight, aes(x = EDays, y = log10(Sig), colour = par_ue))+ 
  geom_point() +
  geom_point(data = PhotoPhysMedLight) + 
  geom_point(data = PhotoPhysHighLight) +
  facet_grid(rows = vars(Ex_WL), cols = vars(ExpSalinity)) +
  labs(x = "elapsed days", y = PhoPhysVar) +
  #ylim(0, 0.5) +
  xlim(0, 14) +
  theme_bw() +
  labs(caption = paste("strain", OneStrain))
ggsave(filename = file.path("Plots", paste(OneStrain, PhoPhysVar, "salinity.png", sep = "_"),fsep = .Platform$file.sep ), plot = PhotoPhysSal, height = 4, width = 6)



```



```{r}

OneStrain = "CZS48M"
LowLightStep = 40
MedLightStep = 160
HighLightStep = 320
GrowthLightStep = 80
GrowthLight = 100
PhoPhysVar = "FvFm"

PhotoPhysGrowthLight <- SolFitShort %>%
  filter(strain == OneStrain) %>%
  filter(CultureID == 'MaBe2341') %>%
  filter(Light_steps == GrowthLightStep) %>%
  #filter(source_salinity == 36) %>%
  mutate(par_ue = as.factor(par_ue)) %>%
  filter(par_ue == GrowthLight)

test <- ggplot(PhotoPhysGrowthLight, aes(x = EHours, y = (FvFm), colour = as.factor(exp_date)))+ 
  geom_point() +
  facet_grid(rows = vars(Ex_WL), cols = vars(ExpSalinity)) 
ggsave(filename = file.path("Plots", paste(OneStrain, PhoPhysVar, "short_salinity.png", sep = "_"),fsep = .Platform$file.sep ), plot = test, height = 4, width = 6)

FemMcR1_450 <- SolFitShort %>%
  #filter(exp_date == ExpDate) %>%
  filter(Light_steps == GrowthLightStep) %>%
  #filter(source == 'MaBe2341')
  filter(CultureID == 'MaBe2341', Ex_WL == '445')

FemEcSal_450 <- SolFitShort %>%
  filter(Light_steps == GrowthLightStep, par_ue == GrowthLight) %>%
  filter(source == 'MaBe2341', Ex_WL == '445')



(plot2 <- ggplot(NULL, aes(EHours, FvFm, colour = as.factor(ExpSalinity))) + 
      geom_line(data = FemMcR1_450) +
      geom_line(data = FemEcSal_450) +
      facet_grid(rows = vars(Ex_WL)) +
      theme_bw()
)

FemMcR1_590 <- SolFitShort %>%
  #filter(exp_date == ExpDate) %>%
  filter(Light_steps == GrowthLightStep) %>%
  #filter(source == 'MaBe2341')
  filter(CultureID == 'MaBe2341', Ex_WL == '590')

FemEcSal_590 <- SolFitShort %>%
  filter(Light_steps == GrowthLightStep, par_ue == GrowthLight) %>%
  filter(source == 'MaBe2341', Ex_WL == '590')

(ggplot(FemEcSal_590, aes(EHours, FvFm, colour = as.factor(ExpSalinity))) + 
      #geom_line(data = FemMcR1_590) +
      geom_line(data = FemEcSal_450) +
      geom_line(data = FemEcSal_590) +
      geom_point(data = FemEcSal_590) +
      geom_point(data = FemEcSal_450) +
      xlim(0, 5) +
      facet_grid(rows = vars(Ex_WL)) +
      theme_bw()
)

EcSal_450 <- ggplot(FemEcSal_450, aes(EHours, FvFm, colour = as.factor(ExpSalinity))) + 
      geom_line(data = FemEcSal_450) +
      geom_point(data = FemEcSal_450) +
      xlim(0, 5) +
    ylim(0.2, 0.3) +
      facet_grid(rows = vars(Ex_WL)) 
EcSal_450

EcSal_590 <- ggplot(FemEcSal_590, aes(EHours, FvFm, colour = as.factor(ExpSalinity))) + 
      geom_line(data = FemEcSal_590) +
      geom_point(data = FemEcSal_590) +
      xlim(0, 5) +
    ylim(0, 0.15) +
      facet_grid(rows = vars(Ex_WL)) 

ggplot() + EcSal_450 + EcSal_590

(plot3 <- ggplot(NULL, aes(EHours, FvFm, colour = as.factor(ExpSalinity))) + 
      #geom_line(data = FemMcR1_590) +
      geom_point(data = FemEcSal_590) +
      facet_grid(rows = vars(Ex_WL)) +
      theme_bw()
)
```



```{r save StrStiMeta, echo=FALSE}
saveRDS(StrStiMeta, file.path(DataOut, 
paste(Project, "PSIParametersStrSti.Rds", sep = ""), fsep = .Platform$file.sep))

saveRDS(StrStiMeta, file.path(DataOut2, 
paste(Project, "PSIParametersStrSti.Rds", sep = ""), fsep = .Platform$file.sep))
```
